### 2021-09-30 analysis/fit_models.Rmd
finished for the day, continue tomorrow

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 10, -5.5, -2)
)

@@

zoom_plt <- ggplot() +
  geom_sf(data = croped_data, fill = "#ededed") +
  geom_sf(data = locations, aes(shape = model), size = 2) +
  geom_sf_text(
    data = selected_sites, aes(label = site),
    nudge_x = c(0.5, 105), nudge_y = c(-0.5, -105)
  ) +
  scale_shape_manual(values = c(2, 17)) +
  theme_nothing() +
  scale_x_continuous(expand=c(0,0)) +
  scale_y_continuous(expand=c(0,0)) +
  labs(x = NULL, y = NULL) +
  theme(
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    text = element_text(family = "URWHelvetica", size = 8)
  )

@@

>>>>

# make plot of model fits
bel_plot <- make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 10, -5.5, -2)
)

bel_plot

@@

zoom_plt <- ggplot() +
  geom_sf(data = croped_data, fill = "#ededed", size = .1) +
  geom_sf(data = locations, aes(shape = model), size = 1.5) +
  geom_sf(data = selected_sites, aes(shape = site, size = 1)) +
  scale_shape_manual(values = c(1, 2, 17, 16)) +
  theme_nothing() +
  scale_x_continuous(expand=c(0,0)) +
  scale_y_continuous(expand=c(0,0)) +
  labs(x = NULL, y = NULL) +
  theme(
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    text = element_text(family = "URWHelvetica", size = 8)
  )

@@

zsl_model_fit
